StatiscalAnalysis_ModelFitting

### 2023-04-07 3 Analysis Scripts/StatiscalAnalysis_ModelFitting.qmd
Edits to full statistical analysis

```{r}
#load needed packages. make sure they are installed.
library(ggplot2) #for plotting
library(ggeffects) #to explore plots  
library(broom) #for cleaning up output from lm()
library(broom.mixed) #for cleaning up output from lmer()
library(here) #for data loading/saving
library(multilevelmod) #mixed effect models
library(tidymodels)
library(lme4)
library(sjPlot) #to help plot models
library(performance) #evaluate model fit and performance

@@

glmer_spec <- 
  linear_reg() %>% 
  set_engine("glmer")

@@

```{r}
lmer_fit_null <- 
  lmer_spec %>% 
  fit(MDR ~ (1|nes), data = data)

lmer_fit_global <- 
  lmer_spec %>% 
  fit(MDR ~ s.lui + s.age + samp + s.nsuccess +(1|nes), data = data)

#Univariate models
lmer_fit_1 <- 
  lmer_spec %>% 
  fit(MDR ~ s.lui +(1|nes), data = data)

lmer_fit_2 <- 
  lmer_spec %>% 
  fit(MDR ~ s.age  +(1|nes), data = data)

lmer_fit_3 <- 
  lmer_spec %>% 
  fit(MDR ~ samp +(1|nes), data = data)

lmer_fit_4 <- 
  lmer_spec %>% 
  fit(MDR ~ s.nsuccess +(1|nes), data = data)

lmer_fit_5 <- 
  lmer_spec %>% 
  fit(MDR ~ s.lui + samp +(1|nes), data = data)

lmer_fit_6 <- 
  lmer_spec %>% 
  fit(MDR ~ s.lui + s.nsuccess +(1|nes), data = data)

lmer_fit_7 <- 
  lmer_spec %>% 
  fit(MDR ~ samp + s.nsuccess +(1|nes), data = data)

lmer_fit_8 <- 
  lmer_spec %>% 
  fit(MDR ~ s.lui*s.age + samp + s.nsuccess +(1|nes), data = data)

lmer_fit_9 <- 
  lmer_spec %>% 
  fit(MDR ~ s.lui + s.age*samp + s.nsuccess +(1|nes), data = data)

lmer_fit_10 <- 
  lmer_spec %>% 
  fit(MDR ~ s.lui + s.age + samp*s.nsuccess +(1|nes), data = data)

lmer_fit_11 <- 
  lmer_spec %>% 
  fit(MDR ~ s.lui + s.age +(1|nes), data = data)

lmer_fit_12 <- 
  lmer_spec %>% 
  fit(MDR ~ s.lui + s.age +  s.nsuccess +(1|nes), data = data)
```

@@

```{r}
AIC_table1 <- compare_performance(lmer_fit_null,lmer_fit_global, lmer_fit_1, lmer_fit_2, lmer_fit_3, lmer_fit_4, lmer_fit_5, lmer_fit_6, lmer_fit_7, lmer_fit_8, lmer_fit_9, lmer_fit_10, lmer_fit_11, lmer_fit_12)

print(AIC_table1)
AIC_table1 = here("4 Results","Tables", "ModelAIC1.rds")
saveRDS(AIC_table1, file = AIC_table1)

plot(compare_performance(lmer_fit_null,lmer_fit_global, lmer_fit_1, lmer_fit_2, lmer_fit_3, lmer_fit_4, lmer_fit_5, lmer_fit_6, lmer_fit_7, lmer_fit_8, lmer_fit_9, lmer_fit_10, lmer_fit_11, lmer_fit_12, rank = TRUE))
```

@@

```{r}
check_model(lmer_fit_11)

@@

model1 <- broom::tidy(lmer_fit_11)
print(model1)

# save fit results table  
model1 = here("4 Results", "Models", "LMERmodel1.rds")
saveRDS(model1, file = model1)

MLp <- plot_model(lmer_fit_11,terms = 's.lui', type="pred", 
           show.data = TRUE, show.values = TRUE, show.p = TRUE,
           title = "", show.legend = TRUE, line.size=1,
           axis.title = c("Landfill Use Index",'Multi-Drug Resistence'))

@@

```{r}
AIC_table2 <- compare_performance(lmer_fit2_null,lmer_fit2_global, lmer_fit2_1, lmer_fit2_2, lmer_fit2_3, lmer_fit2_4, lmer_fit2_5, lmer_fit2_6, lmer_fit2_7, lmer_fit2_8, lmer_fit2_9, lmer_fit2_10, lmer_fit2_11, lmer_fit2_12)

print(AIC_table2)
AIC_table2 = here("4 Results","Tables", "ModelAIC2.rds")
saveRDS(AIC_table2, file = AIC_table2)

plot(compare_performance(lmer_fit2_null,lmer_fit2_global, lmer_fit2_1, lmer_fit2_2, lmer_fit2_3, lmer_fit2_4, lmer_fit2_5, lmer_fit2_6, lmer_fit2_7, lmer_fit2_8, lmer_fit2_9, lmer_fit2_10, lmer_fit2_11, lmer_fit2_12, rank = TRUE))
```

@@

# save fit results table  
model2 = here("4 Results","Models", "LMERmodel2.rds")
saveRDS(model2, file = model2)

@@

Preliminary results

Questions: 
Should over fit models be taken out of performance analysis?
What is the best tool/package to control for small data sets?

>>>>

```{r, warning=FALSE, message=FALSE}
#load needed packages. make sure they are installed.
library(ggplot2) #for plotting
library(ggeffects) #to explore plots  
library(broom) #for cleaning up output from lm()
library(broom.mixed) #for cleaning up output from lmer()
library(here) #for data loading/saving
library(multilevelmod) #mixed effect models
library(tidymodels)
library(lme4)
library(sjPlot) #to help plot models
library(performance) #evaluate model fit and performance
library(see)
library(cAIC4)

@@

glmer_spec <- 
  logistic_reg() %>% 
  set_engine("glmer")

@@

```{r}
glmer_fit_null <- 
  glmer_spec %>% 
  fit(as.factor(MDR) ~ (1|nes), data = data)

glmer_fit_global <- 
  glmer_spec %>% 
  fit(as.factor(MDR) ~ s.lui + s.age + samp + s.nsuccess +(1|nes), data = data)

#Univariate models
glmer_fit_1 <- 
  glmer_spec %>% 
  fit(as.factor(MDR) ~ s.lui +(1|nes), data = data)

glmer_fit_2 <- 
  glmer_spec %>% 
  fit(as.factor(MDR) ~ s.age  +(1|nes), data = data)

glmer_fit_3 <- 
  glmer_spec %>% 
  fit(as.factor(MDR) ~ samp +(1|nes), data = data)

glmer_fit_4 <- 
  glmer_spec %>% 
  fit(as.factor(MDR) ~ s.nsuccess +(1|nes), data = data)

#Multivariate models

glmer_fit_5 <- 
  glmer_spec %>% 
  fit(as.factor(MDR) ~ s.lui + samp +(1|nes), data = data)

glmer_fit_6 <- 
  glmer_spec %>% 
  fit(as.factor(MDR) ~ s.lui + s.nsuccess +(1|nes), data = data)

glmer_fit_7 <- 
  glmer_spec %>% 
  fit(as.factor(MDR) ~ samp + s.nsuccess +(1|nes), data = data)

glmer_fit_8 <- 
  glmer_spec %>% 
  fit(as.factor(MDR) ~ s.lui*s.age + samp + s.nsuccess +(1|nes), data = data)

glmer_fit_9 <- 
  glmer_spec %>% 
  fit(as.factor(MDR) ~ s.lui + s.age*samp + s.nsuccess +(1|nes), data = data)

glmer_fit_10 <- 
  glmer_spec %>% 
  fit(as.factor(MDR) ~ s.lui + s.age + samp*s.nsuccess +(1|nes), data = data)

glmer_fit_11 <- 
  glmer_spec %>% 
  fit(as.factor(MDR) ~ s.lui + s.age +(1|nes), data = data)

glmer_fit_12 <- 
  glmer_spec %>% 
  fit(as.factor(MDR) ~ s.lui + s.age +  s.nsuccess +(1|nes), data = data)
```

@@

```{r}
AIC_table1 <- compare_performance(glmer_fit_null,glmer_fit_global, glmer_fit_1, glmer_fit_2, glmer_fit_3, glmer_fit_4, glmer_fit_5, glmer_fit_6, glmer_fit_7, glmer_fit_8, glmer_fit_9, glmer_fit_10, glmer_fit_11, glmer_fit_12, rank = TRUE, metrics="AICc")

print(AIC_table1)

AIC_table1 %>%
  saveRDS(here("4 Results","Tables", "ModelAIC1.rds"))

plot(compare_performance(glmer_fit_null,glmer_fit_global, glmer_fit_1, glmer_fit_2, glmer_fit_3, glmer_fit_4, glmer_fit_5, glmer_fit_6, glmer_fit_7, glmer_fit_8, glmer_fit_9, glmer_fit_10, glmer_fit_11, glmer_fit_12))
```

@@

```{r}
check_model(glmer_fit_11)

@@

model1 <- broom::tidy(glmer_fit_11)
print(model1)

# save fit results table  
model1 %>%
  saveRDS(here("4 Results", "Models", "LMERmodel1.rds"))

MLp <- plot_model(glmer_fit_11,terms = 's.lui', type="pred", 
           show.data = TRUE, show.values = TRUE, show.p = TRUE,
           title = "", show.legend = TRUE, line.size=1,
           axis.title = c("Landfill Use Index",'Multi-Drug Resistence'))

@@

```{r}
AIC_table2 <- compare_performance(lmer_fit2_null, lmer_fit2_global, lmer_fit2_1, lmer_fit2_2, lmer_fit2_3, lmer_fit2_4, lmer_fit2_5, lmer_fit2_6, lmer_fit2_7, lmer_fit2_8,
                                  lmer_fit2_9, lmer_fit2_10, lmer_fit2_11, lmer_fit2_12, rank = TRUE, metrics="AICc")

print(AIC_table2)

AIC_table2 %>%
 saveRDS(here("4 Results","Tables", "ModelAIC2.rds"))

plot(compare_performance(lmer_fit2_null, lmer_fit2_global, lmer_fit2_1, lmer_fit2_2, lmer_fit2_3, lmer_fit2_4, lmer_fit2_5, lmer_fit2_6, lmer_fit2_7, lmer_fit2_8,
                                  lmer_fit2_9, lmer_fit2_10, lmer_fit2_11, lmer_fit2_12))
```

@@

# save fit results table  
model2 %>% 
  saveRDS(here("4 Results","Models", "LMERmodel2.rds"))

@@
